Scaffolder - Software for Microbial Genome Scaffolding.

### 2011-02-01 text/src/article.tex
Revise scaffolder file processing section

Each scaffolder sequence entry can have multiple attributes which applied in
different order can result in a different sequence. For instance reverse
complementing the sequence then adding inserts will have a different effect
compared with performing these actions in the reverse order. Scaffolder
therefore follows the following protocol for processing each entry in the
scaffold file. \pb

\paragraph{Reverse sort inserts:} If the entry is a sequence and has sequence
inserts these are reverse sorted by insert close position. The insert with the
largest close position is first and and the smallest close position is last.
This is done to preserve the the insert open/close coordinates as they are
added to the scaffold. \pb

\paragraph{Update sequence with insert:} Each insert is added to the sequence
replacing the region specified by the open an close position with the specified
source sequence.\pb

\paragraph{Update sequence start/stop co-ordinates:} If the insert added to the
sequence is a different length than the region replaced the start and stop
co-ordinates of the sequence are correspondingly updated if necessary. E.g. if
a 7 bp insert filled a bp region this would result in a 2bp difference in the
length of the sequence. The stop coordinated would be updated to reflect this.
\pb

\paragraph{Sub-sequence selected:} If the sequence is has start or stop
sequences specified these are used to trip the sequence to these co-ordinates.
\pb

\paragraph{Sub-sequence reverse complemented: } If specified with the reverse keyword the sequence is reverse complemented.
\pb

>>>>

The sequence entry in the scaffold file allows multiple sequence-editting
attributes which when applied in different combinations will result in
different output sequence. An example is reverse complementing the sequence
then follwing adding sequence inserts. Performing these actions in the reverse
order will produce a difference output sequence. This section therefore
outlines the scaffolder protocol for processing sequence entries. \pb

\paragraph{Reverse sort inserts:} If the sequence entry contains a list of
inserts these are reverse sorted by close position. The insert with the
largest close position is first in the list and inserts with the smallest
close position is last. This preserves the original indented coordinates for
insert during the process of adding inserts to the sequence. \pb

\paragraph{Update sequence with insert:} Each insert sequence is processed
according to any specified attributes. The insert is added to the enclosing
sequence in the region specified by the open and close coordinates. \pb

If the insert added to the sequence is a different length than the region
replaced the sequence start and stop co-ordinates are updated. For example if
a 7bp insert replaced a 5bp region the stop coordinate of the enclosing
sequence would be incremented by the 2bp difference. \pb

\paragraph{Triming sequence:} If the sequence is has start or stop sequences
specified these are used to trip the sequence to these co-ordinates
inclusively. \pb

\paragraph{Reverse complement sequence:} If the ``reverse'' keyword is
specified the sequence is reverse complemented. This is final step in
processing the sequence with results in the sequence being returned. \pb
